Multiproduct Batch Processing Time Maximization Problem

### 2023-06-17 (2023) Fraga et al.tex
updating paper
including benchmarks and a benchmark generation function

\emph{Example:} A certain machine must process a batch containing 2 different products: A and B. The production rate of A is 60 g/min while the production rate of B is 40 g/min. The factory has free stock for a maximum of 3000 g of any product, and, according to the maximum stock allowed for each product, an additional 3000 g of product A and 2000 g of product B may be stocked at the factory. There is a demand for 1000 g of product A and 500 g of product B. The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product. A maximum time of 300 minutes of this machine can be allocated for processing this batch. What is the maximum possible time for processing this batch ?

@@

As $T<\textrm{Z}$, then this will certainly be the optimal solution. \\

@@

>>>>

\emph{Example:} A certain machine must process a batch containing 2 different products: A and B. The production rate of A is 60 g/min while the production rate of B is 40 g/min. The factory has free stock for a maximum of 3000 g of any product, and, according to the maximum stock allowed for each product, an additional 3000 g of product A and 2000 g of product B may be stocked at the factory. There is a demand for 1000 g of product A and 500 g of product B. The factory has an outlet that has free space in stock of 1000 g, which can receive a maximum of 600 g of each product. A maximum time of 100 minutes of this machine can be allocated for processing this batch. What is the maximum possible time for processing this batch ?

@@

As $T<\textrm{Z=100}$, then this will certainly be the optimal solution. \\

@@

For building larger benchmarks, we used the following functions: \\

\begin{equation}
\textrm{p}_i = rand()\%30 + 10
\end{equation}

\begin{equation}
\textrm{UD}_i = rand()\%3000 + 800;
\end{equation}

\begin{equation}
\textrm{O} = rand()\%3000 + 500;
\end{equation}

\begin{equation}
\textrm{UO}_i = rand()\%(\textrm{O}-500) + 500;
\end{equation}

\begin{equation}
\textrm{I} = rand()\%5000 + 1000;
\end{equation}

\begin{equation}
\textrm{UI}_i = rand()\%(\textrm{I}-1000) + 1000;
\end{equation}

\begin{equation}
\textrm{Z} = 100;
\end{equation}

Seeking to enable the reproduction of the results, in the computational construction of the benchmarks we used the function srand((unsigned) source), where source is a defined value. To build the results presented in this work, we used source=0. \\
